Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Fixed the issue with PaCMAP model in Figure 13

pacmap_data_gau <- read_rds("data/five_gau_clusters/pacmap_data_five_gau.rds")
gau1_scaled_obj <- gen_scaled_data(
  data = pacmap_data_gau)
pacmap_gau_scaled <- gau1_scaled_obj$scaled_nldr

>>>>

pacmap_data_gau <- read_rds("data/five_gau_clusters/pacmap_data_five_gau.rds")
gau1_scaled_obj <- gen_scaled_data(
  data = pacmap_data_gau)
pacmap_gau_scaled <- gau1_scaled_obj$scaled_nldr |>
  select(PaCMAP1, PaCMAP2, ID)
